{RILS}-{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Moved to JBD format.

	\begin{table}
		\centering
		\begin{tabular}{ll} \\ \hline
			Bacterial representation &   $x' = 20 - x - \frac{x \cdot y}{1 + 0.5 x^2 }$ \\ 
			&   $y' = 10 - \frac{x \cdot y}{1 + 0.5 x^2  }$ \\ \hline
			Shear Flow               &  $\theta' = \cot(\phi)\cos(\theta)$ \\
			&  $ \phi'  = ( \cos^2(\phi) + 0.1 \cdot \sin^2 (\phi)) \sin(\theta) $ \\ \hline
		\end{tabular}
		\caption{Some Strogatz ODE problems.}
		\label{table:strogatz-ODEs}
	\end{table}

@@

Some \textsc{Random} instances are shown in Table~\ref{tbl:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.

\begin{table}
	\centering
	\begin{tabular}{ll} \\ \hline
		random\_04\_02\_0010000\_00 &	$\ln{(x_0 + x_1)}$\\
		random\_07\_02\_0010000\_00 &	$(x_0 + 10)\cdot (x_1 + 1)$\\
		random\_08\_02\_0010000\_00 &	$(x_0 + \ln{x_0})*(x_1 + 10)$\\
		random\_10\_03\_0010000\_02 &	$\ln{(\sqrt{x_0} \cdot x_1/\cos{x_2})}$\\
		random\_12\_04\_0010000\_04 &	$\sqrt{x_3 \cdot \exp{x_1} + \cos{(x_2 \cdot \sin{x_0})}}$\\
		random\_15\_03\_0010000\_04	&   $x_0 \cdot x_1/2 + (\cos{(x_2)} - \pi^2)^2$\\
		\hline
	\end{tabular}
	\caption{Some \textsc{Random} instance problems.}
	\label{table:random}
\end{table}

\subsection{Parameter tuning}
The \textsc{RILS}-\textsc{ROLS} algorithm employs two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$. The first parameter is fixed empirically to 0.001(?), according to the preliminary results.  The second parameter is tuned by monitoring the two errors the algorithm produced on a randomly chosen training set of xx problem instances. Among the following values \{ x, xx, ... \} we chose $tolerance_{error}=?$ for which the largest average $R^2$ and the smallest average RMSE error on all problem instances from the training set are produced. %Note that the training set is chosen randomly with a cardinalty of xx instances.

>>>>

	\begin{table}
		\centering
		\begin{tabular}{ll} \\ \hline
			Bacterial representation &   $x' = 20 - x - \frac{x \cdot y}{1 + 0.5 x^2 }$ \\ 
			&   $y' = 10 - \frac{x \cdot y}{1 + 0.5 x^2  }$ \\ \hline
			Shear Flow               &  $\theta' = \cot(\phi)\cos(\theta)$ \\
			&  $ \phi'  = ( \cos^2(\phi) + 0.1 \cdot \sin^2 (\phi)) \sin(\theta) $ \\ \hline
		\end{tabular}
		\caption{Some \textsc{Strogatz} ODE instances.}
		\label{table:strogatz-ODEs}
	\end{table}

@@

Some \textsc{Random} instances are shown in Table~\ref{table:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.

\begin{table}
	\centering
	\begin{tabular}{ll} \\ \hline
		random\_04\_02\_0010000\_00 &	$\ln{(x_0 + x_1)}$\\
		random\_07\_02\_0010000\_00 &	$(x_0 + 10)\cdot (x_1 + 1)$\\
		random\_08\_02\_0010000\_00 &	$(x_0 + \ln{x_0})*(x_1 + 10)$\\
		random\_10\_03\_0010000\_02 &	$\ln{(\sqrt{x_0} \cdot x_1/\cos{x_2})}$\\
		random\_12\_04\_0010000\_04 &	$\sqrt{x_3 \cdot \exp{x_1} + \cos{(x_2 \cdot \sin{x_0})}}$\\
		random\_15\_03\_0010000\_04	&   $x_0 \cdot x_1/2 + (\cos{(x_2)} - \pi^2)^2$\\
		\hline
	\end{tabular}
	\caption{Some \textsc{Random} instances.}
	\label{table:random}
\end{table}

\subsection{Parameter tuning}
The \textsc{RILS}-\textsc{ROLS} algorithm employs two control parameters, $penalty_{size}$ and $tolerance_{error}$. The first parameter is empirically tuned for considered benchmarks to 0.001 -- this is also used as a default value in the corresponding Python package (package is described in \ref{sec:appendix-1}). The second parameter is negatively correlated with the expected level of noise in input data, i.e., for higher noise the $tolerance_{error}$ takes lower values and vice-versa.
